A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-11-09 discussion.tex
reviewer 1, todo 2 fixed

A threat to external validity is selection bias, where the benchmarks differ systematically from the actual world. Our selection of projects might be biased and therefore we might not have presented patterns that may exist in other projects. Another threat to external validity can be the developers reporting the commits as bug fixing commits while they are not really fixing functionality. Similarly, a commit message might not contain our target keywords while the commit is associated with bug fixing changes.

>>>>

A threat to external validity is selection bias, where the benchmarks differ systematically from the actual world. Our selection of projects might be biased and therefore we might not have presented patterns that may exist in other projects. Another threat to external validity can be the developers reporting the commits as bug fixing commits while they are not really fixing functionality. Similarly, a commit message might not contain our target keywords while the commit is associated with bug fixing changes. Lastly, Rust is a relatively new programming language, and its syntax is prone to evolving over time. Changes in the Rust's grammar, such as the introduction of new keywords like \verb+async/await+ in version 1.39, have the potential to introduce new bugs or modify existing ones. Thus, it is important to consider the language evolution as a potential external threat to the validity of our research findings.
